AFQ-Insight

### 2019-12-16 reports/manuscript/sections/introduction.tex
Clarify voxel size vs diffusion lengths in first paragraph of introduction

Diffusion-weighted Magnetic Resonance Imaging (dMRI) provides a unique view into
the physical properties of the connections that comprise the brain white matter.
While the measurements are usually conducted with voxels at the millimeter
scale, water molecules within each voxel probe the structure of white matter at
the micrometer scale providing important information about the physical
structure of the white matter, including the density of axons and distribution
of nerve fascicle orientations within each voxel \cite{wandell2016clarifying}.
Even though metrics derived from diffusion measurements are ambiguous in terms
of their underlying biological interpretation \cite{Jones2013-xv}, analyzing the
variance in these properties has proven useful in characterizing individual
differences in cognitive function, characterizing differences between
populations and detecting brain abnormalities associated with disease
\cite{Thomason2011-qn}.

>>>>

Diffusion-weighted Magnetic Resonance Imaging (dMRI) provides a unique
view into the physical properties of the connections that comprise
the brain white matter. While the measurements are usually conducted
with voxels at the millimeter scale, water molecules within each voxel
diffuse with characteristic lengths at the micrometer scale, providing
aggregate information about the physical structure of the white matter,
including the density of axons and distribution of nerve fascicle
orientations within each voxel \cite{wandell2016clarifying}. Even though
metrics derived from diffusion measurements are ambiguous in terms
of their underlying biological interpretation \cite{Jones2013-xv},
analyzing the variance in these properties has proven useful in
characterizing individual differences in cognitive function,
characterizing differences between populations and detecting brain
abnormalities associated with disease \cite{Thomason2011-qn}.
